```{r}
#| include: false
#| eval: true

source('R/appdown.r')
```

# Linux `r os_logo('linux')`

Install the following tools to build *{{< var PROGRAM_NAME >}}*:

| Program |
| :-- |
| *GCC* {{< var MIN_GCC_REQUIRED >}} or higher (*gcc* and *gfortran*) |
| *CMake* {{< var CMAKE_MINIMUM_REQUIRED_VERSION >}} or higher (*cmake* and *cmake-extra*) |
| *git* |
| *AppImage* (*libappimage-dev*) |
| *R* (*r-base*, optional) |
| *Quarto* ([https://quarto.org/](https://quarto.org/), optional) |
| *POEdit* (*poedit*, optional) |

Install the following libraries:

```{r}
#| echo: false
#| message: false

linux_libs <- dplyr::as_tibble(
  read.delim("data/linux-libs.txt", sep = "\t", header = TRUE, check.names = FALSE)) |>
  dplyr::mutate_all(markdown_to_kable_cell)

kableExtra::kbl(linux_libs, booktabs = TRUE, linesep = "", escape = FALSE) |>
  kableExtra::kable_styling() |>
  kableExtra::row_spec(seq(2, nrow(linux_libs), 2), background = "#F0F0F0")
```

{{< pagebreak >}}

## Download *wxWidgets* {-}

```{.bash}
git clone https://github.com/wxWidgets/wxWidgets.git --recurse-submodules
```

This should be cloned into a folder next to *{{< var PROGRAM_NAME >}}*.

## Build *{{< var PROGRAM_NAME >}}* {-}

```{.bash include="build-commands.txt" start-line=1 end-line=9}
```

::: {.tipsection data-latex=""}
To create a debug build, pass `-DCMAKE_BUILD_TYPE=Debug` during the configuration stage, and `--config Debug` during the build stage.
You can also pass `-DENABLE_SANITIZERS=TRUE` to enable AddressSanitizer support in debug builds.

If you need to build with local modifications in Git submodules, add `-DALLOW_DIRTY_SUBMODULES=ON` to bypass the clean-check validation.
:::

## Build the AppImage {-}

::: {.tipsection data-latex=""}
The following steps are only required if you are distributing builds outside CI, your local machine, or Eclipse's infrastructure.
:::

```{.bash}
linuxdeploy-x86_64.AppImage --appdir installers/unix/AppDir \
  --executable installers/unix/AppDir/usr/bin/readstudio    \
  -d installers/unix/AppDir/readstudio.desktop              \
  -i installers/unix/AppDir/app-logo.svg                    \
  --output appimage
mv Readability_Studio*.AppImage ./installers/unix
```

Once built, the AppImage will be available in `r menu(c('installers', 'unix'))`.
Apply a GPG signature to it before distributing.
