```{r}
#| include: false
#| eval: true

source('R/appdown.r')
```

# Microsoft^®^ Windows `r os_logo('Windows')`

| Requirements |
| :-- |
| 64-bit Windows {{< var WIN32_REQUIRED >}} (or higher) |
| x86_64 processor |
| {{< var INSTALLED_SIZE_MB >}} MB of disk space |
| {{< var MIN_RAM >}} of RAM ({{< var RAM_RECOMMENDED >}} recommended) |

The *Microsoft Visual C++ runtime* is also required.
This is normally managed via *Windows Update*, but can also be installed manually.
To install, download and run the latest [Microsoft Visual C++ Redistributable](https://learn.microsoft.com/en-us/cpp/windows/latest-supported-vc-redist) installer.

The *Microsoft Edge WebView2 Runtime* is also required.
This is pre-installed on Windows 11 and is normally managed via *Windows Update*, but can also be installed manually.
To install, download and run the latest [Microsoft Edge WebView2 Runtime](https://developer.microsoft.com/en-us/microsoft-edge/webview2/) installer.

## Installing Locally {-}

Run the installer ("ers-setup.exe") as an administrator.
You will be prompted for a user name, where to install the program, and which components to install.
After answering these prompts, continue the installer to completion.

## Installing Remotely {-}

Run the installer ("ers-setup.exe") via a remote tool, such as *Windows^®^ SCCM* (*System Center Configuration Manager*).
Refer to the end of this chapter for available command line options.

## Uninstalling {-}

The program can be uninstalled via the system's **Installed apps** panel or from the command line.

In the installation folder of *{{< var PROGRAM_NAME >}}*, there will be a file named similar to "unins???.exe."
System Admins can run this program remotely to uninstall the program from workstations.

::: {.tipsection data-latex=""}
"unins???.exe" can take parameters, such as `/VERYSILENT`.
:::

## Updating {-}

To upgrade an installation, run the installer ("ers-setup.exe") as an administrator and follow the prompts.
If there is a previous installation of *{{< var PROGRAM_NAME >}}*, then the installer will update it.

::: {.notesection data-latex=""}
If updating a 32-bit edition of *{{< var PROGRAM_NAME >}}* (version 2021 or earlier), you will first need to uninstall the program.
The 64-bit editions default to the 64-bit `r file_path("Program Files")` folder, while earlier editions were installed to the `r file_path("Program Files (x86)")` folder.
Uninstalling any 32-bit editions will ensure that you won't have multiple installations after updating.
:::

## Command Line Options {-}

The installer uses *Inno Setup*, which provides support for silent install and other options.
(This applies to installing, uninstalling, and upgrading.)
To perform a silent install, pass the command line arguments `/SILENT` or `/VERYSILENT`.
For example, the following will run a silent install that will not restart the computer and write its progress to a log file:

```{.bash include="windows-silent.txt"}
```

Available command line options include:

```{r}
#| echo: false
#| message: false

inno_options <- dplyr::as_tibble(
  read.delim("data/innosetup-options.txt", sep = "\t", header = TRUE, check.names = FALSE))

# Convert \n placeholder to actual newlines, then apply linebreak() for makecell support
inno_options[[2]] <- inno_options[[2]] |>
  stringr::str_replace_all(stringr::fixed("\\n"), "\n") |>
  kableExtra::linebreak()

kableExtra::kbl(inno_options, booktabs = TRUE, linesep = "", escape = FALSE) |>
  kableExtra::kable_styling() |>
  kableExtra::column_spec(1, monospace = TRUE) |>
  kableExtra::row_spec(seq(2, nrow(inno_options), 2), background = "#F0F0F0")
```
